\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\setlength{\footskip}{4.08003pt}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge John R. Molina} \\ \vspace{1pt}
    \small \href{https://www.johndev.io}{\underline{johndev.io}} $|$
    \href{https://github.com/rich-txt-editor}{\underline{github.com/rich-txt-editor}} $|$
    \href{mailto:johnrichardmolina@gmail.com}{\underline{johnrichardmolina@gmail.com}} $|$
    \href{https://linkedin.com/in/jrmolin90}{\underline{linkedin.com/in/jrmolin90}}
  \end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Montclair State University}{Montclair, NJ}
      {Bachelor of Science in Computer Science}{Aug. 2022 -- Jan. 2024}
    \resumeSubheading
      {Hudson County Community College}{Jersey City, NJ}
      {Associate of Science in Computer Science }{Aug. 2013 -- May 2016}
  \resumeSubHeadingListEnd

%




%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C/C++, PHP, Python, Bash (Zsh), SQL (MySQL, PL/SQL, SQLite3), Java, Ruby, JavaScript, Swift, HTML/CSS, LaTeX} \\
     \textbf{Frameworks}{: Django, Node.js, Tailwind CSS, Bootstrap, React, Wix, Django Rest Framework, Material-UI, Spring} \\
     \textbf{Developer Tools}{: Git, Docker, Gunicorn, Google Cloud Platform, AWS, NeoVim,  VS Code, PyCharm, IntelliJ, Eclipse} \\
     \textbf{Libraries}{: pandas, NumPy, Seaborn, Matplotlib, Axios, Capybara, RSpec, Regular Expressions}
    }}
 \end{itemize}



%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Programming AI Coding Trainer}{Feb. 2024 -- Present}
      {DataAnnotation Tech}{Remote}
      \resumeItemListStart
        \resumeItem{Conducted extensive training for Large Language Models, with a focus on computer science and programming domains, to enhance the effectiveness of various in-house models.}
        \resumeItem{Performed domain research to train an Artificial Intelligence Model for improved coding prompt responses.}
        \resumeItem{Implemented data-driven evaluation strategies to enhance the precision and reliability of model conversations.}
        \resumeItem{Participated in various coding projects to train two models simultaneously across multiple languages including C, C++, Java, JavaScript, Swift, Python, and Bash.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Development Assistant}{Dec. 2017 -- Aug. 2022}
      {Columbia University, Office of Alumni \& Development Data Management Group}{New York, NY}
      \resumeItemListStart
        \resumeItem{Managed and conducted data integrity efforts by performing data corrections using an Oracle database with PL/SQL and Excel to create a pipeline of up-to-date nonprofit university fundraising data.}
        \resumeItem{I helped exceed fundraising targets of \$3 billion, \$4 billion, and \$5 billion year over year through strategic data management, resulting in deeper donor relationships and 106\% more engaged alumni on average.}
        \resumeItem{Spearheaded accuracy-driven constituent and philanthropic data verification projects using LexisNexis, Initium, and other platforms to ensure the integrity of fundraising-related operations.}
        \resumeItem{Utilizing Salesforce, I spearheaded the delivery of comprehensive data services across the university, while also overseeing a user-facing ticketing system. This system provided top-tier customer service to various schools and departments, ensuring seamless and efficient support.}
        \resumeItem{I worked closely with systems engineers, fundraisers, gift officers, and prospect development teams to optimize data pipeline processes, significantly enhancing fundraising operations and overall efficiency.
}
    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
            {\textbf{www.johndev.io} $|$ \emph{Git, Django, JavaScript, React, SQLite3, Ubuntu Droplet}}{January 2024 -- Present}
            \resumeItemListStart
            \resumeItem{Designed, Developed and currently maintain a Django web app for my software engineering portfolio and blog.}
            \resumeItem{Relational database and Django Rest Framework API implemented to store and display website content.}
            \resumeItem{Frontend light \& dark themes along with tooling written in Tailwind CSS and JavaScript.}
            \resumeItem{Developed a REST API using Django Rest Framework and SQLite3. Implemented CAPTCHA and blog comment rate limiting.}
          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{redis-c} $|$ \emph{C/C++}}{Jun 2024 -- Present}
          \resumeItemListStart
            \resumeItem{Writing a clone of Redis in C and C++ from scratch.}
            \resumeItem{Implementing Systems and Network programming concepts for a load bearing database living in your RAM.}
            \resumeItem{Currently in development.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd





%-------------------------------------------
\end{document}
